DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-05-31 manuscript/manuscript.Rmd
creating table 1 as .tex in small example vignette, and adding it to manuscript as graphic

documentclass     : "apa6"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    includes      :
      in_header: "preamble.tex"
      after_body  : ["figures-alt.tex", "figures-supplementary.tex"]

>>>>

documentclass     : "apa6"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    includes      :
      in_header: "preamble.tex"
      after_body  : ["tables.tex",
                     "figures-alt.tex", 
                     "figures-supplementary.tex"]
